The \dealii Library, Version 9.5

### 2023-06-05 9.5/paper.tex
update funding

M.~Maier was partially supported by NSF Awards DMS-1912847 and DMS-2045636.

@@

The Interdisciplinary Center for Scientific Computing (IWR) at Heidelberg
University has provided hosting services for the \dealii web page.
\todo{Is this still true?}

>>>>

M.~Maier was partially supported by NSF Award DMS-2045636 and and by the
Air Force Office of Scientific Research under grant/contract number
FA9550-23-1-0007.

@@
